True versus apparent shapes of astrophysical bow shocks

### 2017-03-06 papers/Paper1/quadrics-appendix.tex
Move appendices to after references
Automatically generate data for table of tail coefficients
This is done in Rc-revisited-2016.org in the section "Write LaTeX
version of the tail analytic fit for paper".  The results are then
pasted into the latex file.
Minor changes:
* Exchange Figures 2 and 3/
* subindices of eqautions A9 and A10 converted to \mathrm
Missing exchanges to tilded Rc and R90
Add a subsection about Wilkin solution section 5

\appendix
\appendixpage
\addappheadtotoc
\section{Parabola of Revolution}
\label{app:parabola}

@@

\begin{align}
\left(\frac{q'}{q}\right)_{parabola} &= 1+\frac{A\tan^2 i}{2}\\
\left(A'\right)_{parabola} &= \frac{A}{\cos^2 i + \frac{A}{2}\sin^2 i}
\end{align}

@@

\section{Analytic derivation of $R_{90}$ in the Thin Shell model}
\label{app:r90-analytic}

@@

\begin{align}
R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
\left(1-\xi\beta\right)} \\
\implies B &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
\end{align}

>>>>

\appendix
% \appendixpage
% \addappheadtotoc
\section{Parabola of Revolution}
\label{app:parabola}

@@

\begin{align}
\left(\frac{q'}{q}\right)_{\mathrm{parabola}} &= 1+\frac{\tilde{R}_c\tan^2 i}{2}\\
\left(\tilde{R}'_c\right)_{\mathrm{parabola}} &= \frac{\tilde{R}_c}{\cos^2 i + \frac{\tilde{R}_c}{2}\sin^2 i}
\end{align}

@@

\section{Analytic derivation of \texorpdfstring{\boldmath $R_{90}$}{R\_90} in the thin shell model}
\label{app:r90-analytic}

@@

\begin{align}
R_{90} &= \frac{\left(3\xi\beta\right)^{1/2}}{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}
\left(1-\xi\beta\right)} \\
\implies \tilde{R}_{90} &\equiv \frac{R_{90}}{R_0} = \frac{\sqrt{3\xi}\left(1+\beta^{1/2}\right)}
{\left(1+\frac{1}{5}\xi\beta\right)^{1/2}\left(1-\xi\beta\right)}
\end{align}

\section{Derivation of Characteristic Radii in Isotropic Wind/Parallel interaction Problem}
\label{app:ch-rad-Wilkin}

$\tilde{R}_{90}$ is obtained by simply evaluating equation (\ref{eq:R-Wilkin}) at $\theta=\frac{\pi}{2}$.
For the Radius of curvature we follow a similar procedure than the Wind/Wind interaction, but using equation
(\ref{eq:R-Wilkin}) for $R(\theta)$ and inserting the cosecant into the square root.

Expanding the terms of $R(\theta)$ we find the following:

\begin{align}
  \csc^2\theta &\simeq \theta^{-2}\left[1+\frac{\theta^2}{3}\left(1+\frac{\theta^2}{5}\right)\right] \\
  1-\theta\cot\theta &\simeq \frac{\theta^2}{3}\left[1 + \frac{\theta^2}{15}\left(1+\frac{2\theta^2}{21}\right)\right] \\
  \implies \tilde{R}(\theta) \simeq 1 + \frac{\theta^2}{5} + O\left[\theta^4\right]
\end{align}

From equation (\ref{eq:Rcurv}) for the radius of curvature we finally get the numerical value for $\tilde{R_c} = \frac{5}{3}$

%%% Local Variables:
%%% mode: latex
%%% TeX-master: quadrics-bowshock
%%% End:

### 2017-03-06 papers/Paper1/sec-thin-shell.tex
Add a subsection about Wilkin solution section 5

Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:thc-conic})

@@

%Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

@@

>>>>

Finally, using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of
conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (\ref{eq:Thc})

@@

% Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii,
%being $R_0$ the
%easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

@@

\subsection{Special Case: Isotropic Wind/Parallel Flow Interaction Problem}

This problem has already been solved in \citet{Wilkin:1996a} and \CRW{}, which have an explicit form for the shell shape, given by:

\begin{align}
  R(\theta) = R_0\csc\theta\left[3(1-\theta\cot\theta)\right]^{1/2} \label{eq:R-Wilkin}
\end{align}
Where:
\begin{align}
  R_0 = \left(\frac{\dot{M}⁰_wv_w}{4\pi\rho_a v_a^2}\right)^{1/2}
\end{align}
And $\rho_a$ and $v_a$ being the density and the velocity of the Parallel wind, respectively.
The characteristic radii are given by:
\begin{align}
  \tilde{R}_{90} &= \sqrt{3} \\
  \tilde{R}_c &= \frac{5}{3}
\end{align}
The derivation of these values is developed in appendix \ref{app:ch-rad-Wilkin}
